% ------------------------------------------------------------------------------
Array jobs are those that start a batch job or a parallel job multiple times. 
Each iteration of the job array is called a task and receives a unique job ID.
Only supported for batch jobs; submit time $< 1$ second, compared to repeatedly
submitting the same regular job over and over even from a script.

%To submit an array job, use the \texttt{\-t} option of the \texttt{qsub} 
%command as follows:
To submit an array job, use the \option{--array} option of the \texttt{sbatch} 
command as follows:

%\begin{verbatim}
%qsub -t n[-m[:s]] <batch_script>
%\end{verbatim}
\begin{verbatim}
sbatch --array=n-m[:s]] <batch_script>
\end{verbatim}

\textbf{-t Option Syntax:}
\begin{itemize}
\item
\texttt{n}: indicates the start-id.
\item
\texttt{m}: indicates the max-id.
\item
\texttt{s}: indicates the step size.
\end{itemize}

\textbf{Examples:}
\begin{itemize}
\item
\verb+sbatch --array=1-50000 -N1 -i my_in_%a -o my_out_%a array.sh+: submits a job with 50000 elements,
\%a maps to the task-id between 1 and 50K. 
\item
%\texttt{qsub -t 10 array.sh}: submits a job with 1 task where the task-id is 10. 
\texttt{sbatch --array=10 array.sh}: submits a job with 1 task where the task-id is 10. 
\item
%\texttt{qsub -t 1-10 array.sh}: submits a job with 10 tasks numbered consecutively from 1 to 10.
\texttt{sbatch --array=1-10 array.sh}: submits a job with 10 tasks numbered consecutively from 1 to 10.
\item
%\texttt{qsub -t 3-15:3 array.sh}: submits a jobs with 5 tasks numbered consecutively with step size 3
\texttt{sbatch --array=3-15:3 array.sh}: submits a jobs with 5 tasks numbered consecutively with step size 3
(task-ids 3,6,9,12,15).
\end{itemize}

\textbf{Output files for Array Jobs:}

The default and output and error-files are
%\option{job\_name.[o|e]job\_id} and\\
%\option{job\_name.[o|e]job\_id.task\_id}.
\texttt{slurm-job\_id\_task\_id.out}.
%
This means that Speed creates an output and an error-file for each task 
generated by the array-job as well as one for the super-ordinate array-job. 
To alter this behavior use the \option{-o} and \option{-e} option of
%\tool{qsub}. 
\tool{sbatch}. 

For more details about Array Job options, please review the manual pages for 
%\option{qsub} by executing the following at the command line on speed-submit 
%\tool{man qsub}.
\tool{sbatch} by executing the following at the command line on speed-submit 
\texttt{man sbatch}.
