% ------------------------------------------------------------------------------
%						C Sister Facilities
% ------------------------------------------------------------------------------

Below is a list of resources and facilities similar to Speed at various capacities.
Depending on your research group and needs, they might be available to you. They
are not managed by HPC/NAG of AITS, so contact their respective representatives.

\begin{itemize}
    \item
    \texttt{computation.encs} CPU only 3-machine cluster running longer jobs
    without a scheduler at the moment
    \item
    \texttt{apini.encs} cluster for teaching and MPI programming (see the corresponding
    course in CSSE)
    \item
    Computer Science and Software Engineering (CSSE) Virya GPU Cluster. For CSSE 
    members only. The cluster has 4 nodes with total of 32 NVIDIA GPUs (a mix of
    V100s and A100s). To request access send email to \texttt{virya.help AT concordia.ca}.
    \item
    Dr. Maria Amer's VidPro group's nodes in Speed (-01, -03, -25, -27) with additional V100 and P6 GPUs.
    \item
    There are various Lambda Labs other GPU servers and like computers
    acquired by individual researchers; if you are member of their
    research group, contact them directly. These resources are not
    managed by us.

    \begin{itemize}
        \item
        Dr. Amin Hammad's \texttt{construction.encs} Lambda Labs station
        \item
        Dr. Hassan Rivaz's \texttt{impactlab.encs} Lambda Labs station
        \item
        Dr. Nizar Bouguila's \texttt{xailab.encs} Lambda Labs station
        \item
        Dr. Roch Glitho's \texttt{femto.encs} server
        \item
        Dr. Maria Amer's \texttt{venom.encs} Lambda Labs station
        \item
        Dr. Leon Wang's \texttt{guerrera.encs} DGX station
    \end{itemize}

    \item
    Dr. Ivan Contreras' servers (managed by AITS)
    \item
    If you are a member of School of Health (formerly PERFORM Center),
    you may have access to their local 
    \href
    {https://perform-wiki.concordia.ca/mediawiki/index.php/HPC_Cluster}
    {PERFORM's High Performance Computing (HPC) Cluster}.
    Contact Thomas Beaudry for details and how to obtain access.
    \item
    All Concordia students have access to the Library's small
    \href
    {https://library.concordia.ca/technology/sandbox/}
    {Technology Sandbox}
    testing cluster that also runs Slurm. Email \texttt{sean.cooney AT concordia.ca} for details.
    \item
    Digital Research Alliance Canada (Compute Canada / Calcul Quebec),\\
    \url{https://alliancecan.ca/}. Follow
    \href
    {https://alliancecan.ca/en/services/advanced-research-computing/account-management/apply-account}
    {this link}
    on the information how to obtain access (students need to be sponsored
    by their supervising faculty members, who should create accounts
    first). Their SLURM examples are here: \url{https://docs.alliancecan.ca/wiki/Running_jobs}
    
\end{itemize}