% -----------------------------------------------------------------------------
%						C Sister Facilities
% -----------------------------------------------------------------------------
\section{Sister Facilities}
\label{sect:sister-facilities}

Below is a list of resources and facilities similar to Speed at various capacities.
Depending on your research group and needs, they might be available to you. They
are not managed by HPC/NAG of AITS, so contact their respective representatives.

\begin{itemize}
    \item
    \texttt{computation.encs} is a CPU-only 3-machine cluster running longer jobs without
    a scheduler at the moment. Shares the same EL7 software tree as Speed's EL7 nodes
    as well as lab desktops. See \url{https://www.concordia.ca/ginacody/aits/public-servers.html}.

    \item
    \texttt{apini.encs} cluster for teaching and MPI programming (see the corresponding
    course in CSSE), managed by CSSE.

    \item
    Computer Science and Software Engineering (CSSE) Virya GPU Cluster. For CSSE
    members only. The cluster has 4 nodes with total of 32 NVIDIA GPUs (a mix of
    V100s and A100s). To request access send email to \texttt{virya.help AT concordia.ca}.
    This includes an Atlas Analytics partition of Dr.~Mahdi Husseini.

    \item
    Dr.~Eugene Belilovsky hightower Exxact, and megatower graphcore clusters.

    \item
    Dr.~Maria Amer's VidPro group's nodes in Speed (-01, -03, -25, -27) with additional V100 and P6 GPUs.

    \item
    There are various Lambda Labs other GPU servers and like computers
    acquired by individual researchers; if you are member of their
    research group, contact them directly. These resources are not
    managed by us.

    \begin{itemize}
        \item Dr.~Amin Hammad's \texttt{construction.encs} Lambda Labs station
        \item Dr.~Hassan Rivaz's \texttt{impactlab.encs} Lambda Labs station
        \item Dr.~Nizar Bouguila's \texttt{xailab.encs} Lambda Labs station
        \item Dr.~Roch Glitho's \texttt{femto.encs} server
        \item Dr.~Maria Amer's \texttt{venom.encs} Lambda Labs station
        \item Dr.~Leon Wang's \texttt{guerrera.encs} DGX station
    \end{itemize}

    \item
    Dr.~Ivan Contreras' 4 Operations Research group servers (managed by AITS).

    \item
    If you are a member of School of Health (formerly PERFORM Center),
    you may have access to their local
    \href{https://perform-wiki.concordia.ca/mediawiki/index.php/HPC_Cluster}{PERFORM's High Performance Computing (HPC) Cluster}.
    Contact Thomas Beaudry for details and how to obtain access.

    \item
    All Concordia students have access to the Library's small
    \href{https://library.concordia.ca/technology/sandbox/}{Technology Sandbox}
    testing cluster that also runs Slurm. Email \texttt{sean.cooney AT concordia.ca} for details.

    \item
    Digital Research Alliance Canada (Compute Canada / Calcul Quebec),\\
    \url{https://alliancecan.ca/}. Follow
    \href{https://alliancecan.ca/en/services/advanced-research-computing/account-management/apply-account}{this link}
    on the information how to obtain access (students need to be sponsored
    by their supervising faculty members, who should create accounts first).
    Their SLURM examples are here: \url{https://docs.alliancecan.ca/wiki/Running_jobs}

\end{itemize}